%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  System        : 
%  Module        : 
%  Object Name   : $RCSfile$
%  Revision      : $Revision$
%  Date          : $Date$
%  Author        : $Author$
%  Created By    : Robert Heller
%  Created       : Sat Mar 4 08:39:57 2023
%  Last Modified : <230415.1039>
%
%  Description 
%
%  Notes
%
%  History
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    Copyright (C) 2023  Robert Heller D/B/A Deepwoods Software
%			51 Locke Hill Road
%			Wendell, MA 01379-9728
%
%    This program is free software; you can redistribute it and/or modify
%    it under the terms of the GNU General Public License as published by
%    the Free Software Foundation; either version 2 of the License, or
%    (at your option) any later version.
%
%    This program is distributed in the hope that it will be useful,
%    but WITHOUT ANY WARRANTY; without even the implied warranty of
%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%    GNU General Public License for more details.
%
%    You should have received a copy of the GNU General Public License
%    along with this program; if not, write to the Free Software
%    Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%
% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,twoside]{article}
\usepackage{graphicx}
\usepackage{mathptm}
\usepackage{times}
\usepackage{makeidx}
\usepackage{ifpdf}
\usepackage{footmisc}
\ifpdf
\usepackage[pdftex,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue,
            unicode
           ]{hyperref}
\else
\usepackage[ps2pdf,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue,
            unicode
           ]{hyperref}
\usepackage{pspicture}
\fi
\usepackage{url}
\pagestyle{headings}
\makeindex
\emergencystretch=50pt
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\title{ESP32 T7S3 MultiFunctionUniversalTurnout Kit Instructions}
\author{Robert Heller \\ The Country Robot \\ Wendell, MA, USA}
\date{\today}
\begin{document}
\maketitle

This is a circuit board that supports a Lily Go T7 S3 (mini32) board to manage
multiple model railroad functions as a LCC\footnote{Layout Command Control --
see NMRA's 9.7.x standards, available on the NMRA website
\url{https://www.nmra.org/lcc}.} node. This board provides the following 
functions:

\begin{itemize}
\item Four turnout motors with point sense.  This board uses one of four 
turnout driver daughter boards:
\begin{enumerate}
\item Stall-motor drivers, suitable for Circuitron Tortoise and similar slow 
motion, stall motor switch machines.
\item Twin-coil drivers, suitable for Atlas or Peco snap action switch 
machines.
\item Single-coil drivers, suitable for Kato snap action switch machines.
\item Servo drivers, suitable for using RC control servos to operate turnouts.
\end{enumerate}
\item Four CT coil occupancy detectors.
\item Four driver circuits, suitable for indicator LEDs, decoupling 
electromagnets, solenoids, relays, etc.
\item Four Schmitt-trigger button inputs.
\item Sixteen signal lamp drivers.
\end{itemize}

\clearpage
\input{Assembly.tex}
\input{Downloadables.tex}
\input{GeneralWiring.tex}
\section{Application Notes}

In this section I will present four applications:

\begin{enumerate}
\item One end of a siding with local (facia panel) and remote (eg dispatcher
or CTC) control in Section~\ref{sect-appl:siding}.
\item A Yard Throat with track selection in 
Section~\ref{sect-appl:yardthroat}. 
\item A crossing with an interchange track in 
Section~\ref{sect-appl:crossinginterchange}.
\item Automatic Block Signals in Section~\ref{sect-appl:ABS}.
\end{enumerate}

\input{ApplNote_Siding.tex}
\input{ApplNote_YardThroat.tex}
\input{ApplNote_Crossing.tex}
\input{ApplNote_ABS.tex}

\end{document}
